Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-17 paper/paper.tex
Add building correspondence function + details

The SLU map contains 
The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The SLU data is aqqcuired by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Property limits and building features have a position accuracy requirement of 5 meters.
(Lantmäteriet, 2019)

@@

@@

>>>>

The SLU map contains building features and property limits, but no road data.
The SLU map is maintained by The Swedish National Land Survey (Swedish: Lantmäteriet).
The SLU data is aqqcuired by land surveying methods such as GPS or DGNSS positioning, or by reproduction of features from ortophoto or stereo mapping from 3D aerial images.
The map is updated continously by Lantmäteriet, in conjoncture with the forming or reforming of property.
Property limits and building features have a position accuracy requirement of 5 meters.
(Lantmäteriet, 2019)

@@

\section{Dataset quality evaluation}

//TODO: Feature mapping, how to, first of all

\subsection{Building correspondence}

The building footprint correspondence will be evaluated using a similarity function that assesses the turning funciton and relative area overlap. The similarity function between any building in the OSM data set and any building in the SLU datasets will be defined as a function of their respective footprints ($foot_{OSM}, foot_{SLU}$), as follows:
$S(foot_{OSM}, foot_{SLU}) = S_{T}(foot_{OSM}, foot_{SLU}) + S_{RO}(foot_{OSM}, foot_{SLU})$, where $S_{T}$ measures the difference in turning function and $S_{RO}$ measures the relative overlap between the footprints.

\subsection{Turning function definition}

The turning function was first defined by Arkin et al. (1991), as a method for measuring the similarity of two polygons. The Turning funciton $T_c(l)$ measures the cumulative angle of the polygon's counter-clockwise tangent, as a function of the cumulative normalized length l. This project uses the turning function as it is defined by (Fan et al., 2014). For a polygon with vertices ${v_1 ... v_n}$ and line segments ${e_1 ... e_n}$ It is defined as follows.
Fix a starting vertex $v_1$.
The tangent angle at $v_1$ is $\theta_{n,1}$. This is the angle between the neighbouring line segments $e_n$ and $e_1$.
For any $i$ such that $i>1$ and $n<i$, the tangent angle at $v_i$ is recursively defined as: $\theta_{i, i-1} = \theta_{n,1} + \sum^{i}_{k=1} \theta_{k, k-1}$
The turning function has some nice geometric properties, in that it is invariant to both rotation and scaling of the polygon. The function contains no information of the orientation of the polygon, only of the relative angle between successive line segments, thus it does not change under roation. It also measures only the normalized cumulative length, which does not change under scaling.
The similarity of two polygons A and B in terms of their turning function is defined as their distance of their cumulative turning functions: $S_{T}(A, B) = 1 - (\int^{1}_{0} T_{C,A}(l) - T_{C,B}(l) dl)^{1/2}$.
The value range of $S(A, B)$ will be 0 to 1, where $S(A,B) = 1$ if the polygons are identical.

//TODO: Completeness by building area, quotation

\subsection{Correspondence by building area}

(Fan et al., 2014) further discussed how the relative overlap in building area can be used to determine building correspondence between datasets. The relative building overlap between the OSM and SLU datasets will be defined as folows, given the footprints of any building in the OSM set ($foot_{OSM}$) and the SLU set ($foot_{SLU}$):

$S_{RO}(foot_{OSM}, foot_{SLU}) = \frac{A_{Overlap}}{min(A_{foot_{OSM}}, A_{foot_{SLU}}))}$

For this project the relative overlap will be used both to find possible matching building candidates, and as a term in their similarity function.

//TODO: Finding identical points

//TODO: Point proximity for positional accuracy

//TODO: Cite biljecki
When presenting CityGML geometric errors, Biljecki recommends to obtain a measure of the distribution of error, introduce a tolerance and calculate the number of features or segments that fall within this tolerance. We can used this as a complementary statistic to the average error and error variance.

@@

\bibitem{arkin-91}
Arkin E.M., Chew L.P., Huttenlocher D.P., Kedem K. and Mitchell J.S.B. 1991. An Efficiently Computable \\
Metric for Comparing Polygonal Shapes. In: IEEE Transaction on Pattern Analysis and Machine \\
Intelligence, Vol. 13, No. 3, March 1991. \\
